\input{Formatting/Elections_Manual-Preamble.tex}

\article[Elections Board]
\section[Purpose]
\subsection The Election Board shall coordinate and exercise jurisdiction over all ASWWU elections, subject to appeal to the Senate.
\subsection The Election Board shall operate the polls, count the ballots, and maintain permanent records of all elections.
\subsection The Election Board shall be responsible for notifying the candidates of the rules pertaining to electioneering and campaign practices.
\section[Structure]
\subsection The chairman of the Election Board shall be the Executive Vice President. If the Executive Vice President is running for an executive position, the President shall appoint a new Election Board chair, subject to ratification by Senate.
\subsection The board shall consist of the chair, the ASWWU Sponsor, and three (3) members nominated by the outgoing President and shall be ratified by the Senate for the following year. The term of office shall start the first day of classes following the year they are selected and shall end at the end of the school year. If any one of the nominated members of the election board is not enrolled or does not return the following year, a new member may be nominated by the current ASWWU President and be ratified by the Senate.
\subsection During the Senate elections, two (2) additional members shall be provided by the ASWWU Executive Cabinet. During the executive elections, two (2) additional members shall be provided by the Senate. If additional help for operating the polls and counting ballots is needed, the Parliamentarian may select up to three (3) additional people to serve on the Election Board as per the approval of the President.
\subsection Any Election Board member who wishes to run for office must resign from the Election Board before declaring their candidacy or they will not be put on the official ballot.
\subsection The Webmaster shall assist the elections board as a non-voting member. 

\article[Elections]

\section[Declarations of Candidacy]
\subsection Appendix A shall consist of the official Declaration of Candidacy and Petition used for all candidates wishing to become an ASWWU Senator.
\subsection Appendix B shall consist of the official Declaration of Candidacy used for all candidates wishing to become the ASWWU President, Executive Vice President, Social Vice President, or Spiritual Vice President.
\section[Campaign Practices]
\subsection No electioneering or campaign posters will be allowed within a fifty (50)-foot radius or sight of any polling location.
\subsection In addition to the other requirements listed in Article II, Section 2 of the Elections Board Manual, all campaign related events, media, and other promotional items to be displayed and or distributed in the residence halls must be approved by a dean of the corresponding residence hall.
\subsection Campaign practices must not, in any way, cause destruction to person or property.
\subsection All campaign posters must receive the “Approved to Post” stamp from the Student Administration office.
\subsection Each candidate is responsible for removing all campaign posters within twenty-four (24) hours of the polls closing
\subsection Endorsements and/or unequal access to platforms and/or speaking events may not be given by official campus organizations or leaders.
\subsection Endorsements, explicit or implicit, may not be expressed by candidates.
\subsection Each candidate shall comply with all rules and regulations present in this manual and issued by the Elections Board.
\subsection Only candidates whose names appear on the official ballot will be allowed to participate in forums sponsored by the ASWWU.
\subsection Endorsements, explicit or implicit, may not be expressed by members of ASWWU Cabinet.
\section[Ballots]
\subsection The Primary Ballot shall include all candidates who officially declared candidacy before the Declaration of Candidacy deadline.
\subsection A General Ballot shall include all candidates remaining after the primary, should it occur. 
\subsection A space for write-in votes for each office will be provided on all general and Senate election ballots. There shall be no write-in space on primary ballots.
\subsection Official ballots will be posted on the ASWWU website twenty-four (24) hours before the polls open.
\section[Polling]
\subsection Polling shall be conducted during CommUnity on election day. Ballots may be received for a period of up to thirty (30) minutes after the conclusion of CommUnity. Other polling stations shall be set up on campus at the discretion of the Election Board.
\subsection ID numbers shall be provided by the voter on each ballot cast to ensure against voter fraud.
\section[Certification]
\subsection The Election Board shall count the ballots and certify the election of the successful candidates.
\subsection The majority vote shall constitute election in any case.
\subsection The Election Board Chairman shall attempt to notify newly elected candidates within twenty-four (24) hours after polls close.
\subsection The names of the candidates elected shall be entered in the official minutes of the Senate. The Election Board Chairman shall submit a report to the Senate of the election results at the first Senate meeting following the election. The results of elections shall be printed in the first issue of The Collegian following the elections.
\subsection The Election Board shall maintain a permanent record of all elections, including the names of all candidates and the number of votes received by each candidate.
\subsection The ballots after each ASWWU election shall be stored in a locked file cabinet in the office of the ASWWU Sponsor who resides on the Election Board. The Election Board will be the only group to have access to this file cabinet. The votes shall be kept for one (1) year after which time they shall be destroyed by the Election Board Chair.
\subsection When the Election Board Chair submits its report of the election results to the Senate, the report shall contain the number of votes each official candidate received and what percentage that number is of the total votes that were received for that office. All write-in votes shall also be included.
\section[Online Elections]
\subsection The Election Board Chair shall be in charge of the online elections.
\subsection Paper ballots shall be checked against online ballots to ensure votes are not cast twice.
\subsection Online polls shall be open during Election Day from 8:00 a.m. to 8:00 p.m.

\article[Senate Elections]
\section[Time of Elections]
\subsection All Senate seats shall stand open for election each October.
\subsection A single election shall be held within the first three (3) weeks of winter and spring quarters when an eligible member of the ASWWU wishes to challenge a seat under ASWWU Bylaws Title 2, Article III, Section 5, or when a vacant seat is contested under ASWWU Bylaws Title 2, Article III, Section 4.
\subsection Elections shall be held not more than ten (10) days after the close of the filing periods for Declarations of
Candidacy.
\subsection A primary may be held when determined by the Election Board to be necessary, but in no case shall a primary election reduce the number of candidates on the official ballot to fewer than two (2) for each seat.
\subsection Primary elections, if held, will be on the Tuesday following the close of the filing period and prior to the election.
\section[Filing of Declarations]
\subsection Each person who wishes to be listed on the official ballot must file an Official Declaration of Candidacy (Appendix A) with the Elections Board. All districts require petitions of twenty (20) signatures. Signatures must come from members of the district which is represented by the seat.
\subsection The filing period for the October election shall begin during the first full week of fall quarter. The filing period for the winter and spring elections, if needed, shall open on the first Monday of the second full week of school in those quarters
\subsection The filing period for declarations shall continue for seven (7) days and shall end at the close of the regular business hours on the day indicated.
\subsection The Faculty District representatives shall be elected by the faculty through the WWU nomination committee. 
\subsection The Staff District representatives shall be elected by the staff through the WWU Staff Council.
\section[Senate Ballots]
\subsection The Election Board shall draw up the ballot and coordinate the Senate election.
\subsection The ballot shall be divided into Senate districts, and ASWWU members shall vote only on the names of the candidates within their own districts. 

\article[Executive Officer Elections]
\section[Time of Election]
\subsection The General Assembly shall be held the second-to-last CommUnity of winter quarter.
\subsection Primary Elections shall be held for all positions where more than two (2) candidates are running for a specific office.
\subsection The Primary Election shall be on the Tuesday preceding the ASWWU CommUnity.
\subsection The Campaigning period shall begin the day following the submissions deadline for the ASWWU Executive Elections Declaration of Candidacy.
\section[\textit{Collegian} Responsibilities]
\subsection \textit{The Collegian} shall publish the platform of any candidate meeting the editor's deadline. Platforms shall be published the Thursday following the opening of the campaign period.
\subsection If a primary election is needed, \textit{The Collegian} shall publish the names of all candidates on the official ballot for the primary election on the Thursday prior to the primary elections.
\subsection \textit{The Collegian} shall also publish the names of all the candidates on the official ballot for the general election on the Thursday prior to the general election.
\section[Filing]
\subsection The filing period shall extend from the first day of winter quarter to Monday of the third week of winter quarter at 5 pm.
\subsection In a case where no declarations of candidacy are received for a position, the filing deadline, for that position only, will be extended by one (1) week. If no candidates have filed for a position following the extended filing period, the Executive Cabinet will decide by majority vote on two (2) names to be place on the official ballot.
\subsection If a position for candidacy is or becomes uncontested at or after the declaration cutoff date, any number of persons may declare candidacy, until 5 pm the day prior to primary elections.
\subsection Each person who wishes to officially run for an elected office of the Executive Committee must file an Official Declaration of Candidacy (Appendix B) with the Election Board.
\subsection In the case where a declaration for candidacy is filed late according to the deadline stipulated above, due to an error on the part of the Elections Committee, the prospective candidate(s) may appeal to the Senate with a G.L. bill requesting acceptance as an official candidate. Senate must approve of the bill by a two-thirds majority. This shall not apply to cases occurring under 3.3.
\section[Positions Involved and Requirements]
\subsection The Executive Cabinet elections are for the positions of President, Executive Vice President, Social Vice President, and Spiritual Vice President.
\subsection All candidates wishing to run for office must run alone.
\subsection All candidates must meet a minimum requirement of cumulative 3.0 GPA on a 4.0 scale.
\subsection Each candidate must not be on citizenship probation.
\subsection All candidates must take twelve (12) credit hours on main campus spring quarter of their campaigning year to be eligible for candidacy.
\subsection The Appeals Board set up in the Personnel Manual, Title I, Article 1, Section 5 shall have the power to consider and grant exceptions to Article IV Section 4.5 on a case-by-case basis.
\subsection The elected Executive Officers must maintain at least twelve (12) credit hours per quarter for the duration of their term, unless otherwise approved by Student Employment. 

\article[Portland Elections]
\section[Declarations of Candidacy]
\subsection See Article II, Section 1.
\section[Campaign Practices]
\subsection See Article II, Section 2. 
\subsection Campaign posters displayed on the Portland campus do not need the “Approved to Post” stamp from the Student Administration office.
\section[Ballots]
\subsection See Article II, Section 3.
\subsection For executive positions there are no online voting ballots for Portland.
\section[Polling]
\subsection During the general assembly, ballots with the names of all the candidates will be passed out to students to record their votes.
\section[Certification]
\subsection The existing Portland Executive Officers and the Portland Sponsor shall count the ballots and the majority vote shall constitute election in any case.
\section[Senate Elections]
\subsection See Article III, Section 1.
\section[Filing of Declarations for Senate]
\subsection See Article III, Section 2.
\section[Senate Ballots]
\subsection See Article II, Section 3.
\subsection Portland Senate Elections can be held at the Portland Executive Officer’s discretion at an assembly. Senators must submit Declarations of Candidacy to the main campus before elections take place.
\section[Executive Officer Elections]
\subsection Filing occurs when any student that is interested in running for any office approaches the current Portland President and explains which office they will be running for. The Portland President will then announce the candidates running two (2) weeks prior to the elections.
\subsection Executive officers shall all be elected at an assembly during spring quarter.
\section[Positions Involved and Requirements]
\subsection See Article IV, Section 4. 

\article[Implementation]
\section[Elections Concerns]
\subsection Concerns regarding elections practices may be brought to the Elections Board by any member of the ASWWU.
\section[Rulings]
\subsection The Elections Board shall meet to discuss any concerns brought to its attention.
\subsection If the concern involves a candidate’s behavior, the Elections Board shall, after its own meeting, work with the candidate to resolve the situation. If no acceptable resolution can be reached, the Elections Board shall have the authority to remove the candidate’s name from the official ballot.
\subsection If the concern involves another party, the Elections Board shall, after its own meeting, recommend an appropriate course of action to the relevant governing body.

\article[Amendments]
\section Changes to the Elections Manual shall follow Title I, Article VI, in the ASWWU Bylaws. 

\nolinenumbers

\newpage

\article[Appendices]

\paragraph[Appendix A: Senate Declaration of Candidacy]

ASWWU Senate is the legislative branch of Walla Walla University's student government. Members of the ASWWU Senate are divded into ten (10) districts. Each district elects two (2) senators to represent them. As a Senator, you will be involved in the parliamentarian process and have direct influence on how ASWWU business is conducted.

To be a Senator you must:
\begin{enumerate}[leftmargin=1.5cm]
\item Be an undergraduate student in good standing enrolled for at least 6 quarter hours.
\item Submit a petition of at least 20 signatures (or 10 signatures for District 10) you represent.
\item Submit a Work Authorization form completed by the Student Employment Center.
\end{enumerate}

As a Senator you will be expected to:
\begin{enumerate}[leftmargin=1.5cm]
\item Spend 2-3 hours per week in a Senate meeting and communicating with your constituents.
\item Have sufficient knowledge of the ASWWU governing documents. (These will be supplied upon election.)
\item Provide a well-informed representation of your constituents' views on campus issues.
\end{enumerate}

\vspace*{3mm}

\begin{center}
\Large Declaration of Candidacy
\end{center}

\doublespacing

I \rule{7cm}{0.15mm} do hereby declare my candidacy for the ASWWU Senate in district \rule{2cm}{0.15mm}.
I understand that I must comply with all stated policies governing ASWWU elections as described in Article II, Section 2, and Article III, Section 2 of the ASWWU Elections Manual. I have read and understand the qualifications and job responsibilities expected of incoming senators as listed above. Furthermore, I acknowledge that I am an undergraduate student in good standing, am enrolled for at least six-quarter hours and if elected, will perform my responsibilities as a Senator to the best of my abilities.

\vspace*{-8mm}

\begin{align*}
\begin{split}
\textrm{Signed} \; &\rule{6cm}{0.15mm}\\[+4mm]
\textrm{Local Address} \; &\rule{6cm}{0.15mm}
\end{split}
\quad
\begin{split}
\textrm{Date} \; &\rule{3cm}{0.15mm}\\[+4mm]
\textrm{Phone} \; &\rule{3cm}{0.15mm}
\end{split}
\end{align*}
\singlespacing

\vspace*{-5mm}

\textit{This completed application must be returned to the ASWWU office (Rm. \#105) in the bottom of Kellogg Hall (cafeteria) by the close of business (5 P.M.) on the second Tuesday of Fall Quarter.}

\vspace*{3mm}

\textbf{Districts}
\begin{align*}
\begin{split}
&\textrm{1. Sittner \nth{1} \& \nth{2} Floor / Meske}\\
&\textrm{2. Sittner \nth{3} \& \nth{4} Floor}\\
&\textrm{3. Conard}\\
&\textrm{4. Foreman}\\
&\textrm{5. Mountain View / Birch Apartments}\\
\end{split}
\begin{split}
&\textrm{6. Hallmark/Faculty Court/University-Owned Housing}\\
&\textrm{7. Off-Campus}\\
&\textrm{8. Portland}\\
&\textrm{9. Faculty}\\
&\textrm{10. Staff}\\
\end{split}
\end{align*}

\newpage

\begin{center}
\Large{Petition of Signatures}
\end{center}

\normalsize

\vspace*{5mm}

We, the undersigned, do reside in district \rule{1cm}{0.15mm}, and do approve the candidacy of \rule{5cm}{0.15mm} to represent us as our ASWWU Senator.

Please provide the 20 signatures below.

\doublespacing

\begin{align*}
\begin{split}
\textrm{1.} \; &\rule{6cm}{0.15mm}\\
\textrm{2.} \; &\rule{6cm}{0.15mm}\\
\textrm{3.} \; &\rule{6cm}{0.15mm}\\
\textrm{4.} \; &\rule{6cm}{0.15mm}\\
\textrm{5.} \; &\rule{6cm}{0.15mm}\\
\textrm{6.} \; &\rule{6cm}{0.15mm}\\
\textrm{7.} \; &\rule{6cm}{0.15mm}\\
\textrm{8.} \; &\rule{6cm}{0.15mm}\\
\textrm{9.} \; &\rule{6cm}{0.15mm}\\
\textrm{10.} \; &\rule{6cm}{0.15mm}\\
\end{split}
\begin{split}
\textrm{11.} \; &\rule{6cm}{0.15mm}\\
\textrm{12.} \; &\rule{6cm}{0.15mm}\\
\textrm{13.} \; &\rule{6cm}{0.15mm}\\
\textrm{14.} \; &\rule{6cm}{0.15mm}\\
\textrm{15.} \; &\rule{6cm}{0.15mm}\\
\textrm{16.} \; &\rule{6cm}{0.15mm}\\
\textrm{17.} \; &\rule{6cm}{0.15mm}\\
\textrm{18.} \; &\rule{6cm}{0.15mm}\\
\textrm{19.} \; &\rule{6cm}{0.15mm}\\
\textrm{20.} \; &\rule{6cm}{0.15mm}\\
\end{split}
\end{align*}

\newpage

\paragraph[Appendix B: Executive Declaration of Candidacy]

\begin{center}
\Large Executive
\end{center}

DECLARATION OF CANDIDACY\\
I, \rule{4cm}{0.15mm}, would like to be considered as an official candidate in the ASWWU Executive Elections for the position of \rule{6cm}{0.15mm} (President, Executive Vice-President, Spiritual Vice-President, or Social Vice-President).\\
I recognize that my declaration will not be accepted without the following information:
\vspace*{-5mm}
\begin{flalign*}
\qquad \textrm{Address:} \; \rule{7cm}{0.15mm} &&\\
\qquad \textrm{Phone:} \; \rule{7cm}{0.15mm} &&\\
\qquad \textrm{Email:} \; \rule{7cm}{0.15mm} &&\\
\end{flalign*}

\vspace*{-15mm}

\singlespacing

With my signature, I certify that I am an official member of the ASWWU. By Completing and signing this form, I agree to abide by all of the following restrictions in regards to the ASWWU Executive Elections, February 27, 2018.
\begin{itemize}
\item Declarations are due by January 22 at 5:00 PM in the ASWWU office in the bottom of Kellogg Hall.
\item Candidates are recommended to talk with current ASWWU officers before filing.
\item Campaigning will begin on January 23, 2018, the day following the due date for this declaration.
\item Campaign methods must not, in any way, cause destruction to person(s) or property.
\item All campaign posters must receive the “Approved to Post” stamp in the Student Administration office at the bottom of Kellogg Hall.
\item Campaign posters will not be allowed within fifty feet or sight of the polls and must comply with the University’s policies.
\item Each candidate is responsible for removing all campaign posters within 24 hours of the polls closing.
\item Each candidate remaining after the primary election, if necessary, is allowed to give a speech at the
\item ASWWU General Assembly to be held February 27, 2018, at CommUnity.
\item Each candidate is allowed to publish a statement in \textit{The Collegian}.
\item Each candidate shall comply with all rules, regulations, and rulings issued by the Elections Board.
\item Each candidate must meet a minimum GPA requirement of 3.0 on a 4.00 scale.
\item Each candidate must not be on citizenship probation.
\item All candidates must take the required number of credit hours on main campus spring quarter of their campaigning year to be eligible for candidacy.
\item The elected Executive Officers must maintain at least twelve (12) credit hours per quarter for the duration of their term, unless otherwise approved by Student Employment. 
\end{itemize}

\vspace*{7mm}

Signature: \rule{7cm}{0.15mm}

\end{document}
