\input{Formatting/Personnel_Manual-Preamble.tex}

\title[Human Resources]

    \article[Employment Eligibility]
        \section To hold an elected or non-elected position in the ASWWU, an individual must:
            \subsection Be a student of Walla Walla University
            \subsection Be enrolled for a minimum of six (6) credit hours, and
            \subsection Have and maintain a GPA above 2.5 on a 4.0 scale.
            \subsection Be a dues paying member of the ASWWU, and
            \subsection Physically attend classed on a Walla Walla University campus.

        \section If an individual elected to or employed by the ASWWU does not maintain his/her eligibility status or is put on citizenship probation, he/she will be asked to step down from his/her position.
        \section Faculty and staff representatives on committees are volunteers and should be in good standing with Walla Walla University. If they are put on probation, they will be asked to step down.
        \section Separate eligibility requirements for the elected executive officers (ASWWU President, EVP, Social VP and Spiritual VP) are found in the Elections Manual, Article IV, Section 4.
        \section In special circumstances, an appeals process can be filed with the Chief Justice. In this case, the Chief Justice, the ASWWU President, the Senate Personnel Committee Chair, the Diversity and Wellness Officer, and the ASWWU Sponsor shall meet to discuss any exceptions made to the requirements in Title 1, Article 1, Section 1 and come to a decision with a 2/3 vote margin.
            \subsection The Senate shall be notified of any appeals made under these circumstances

    \article[ASWWU Positions]
        \section All ASWWU Positions fall under one of three categories of employment: Full-Time Position, Ad Hoc Position, and Contract Position. These titles are defined in Title II, Article 1 of this document. 

    \article[Hiring Process]
        \section[Hiring Practices]
        The ASWWU hires non-elected staff members based on the person’s ability to perform the duties listed in the respective job descriptions, to serve the ASWWU organization, and to represent the students of Walla Walla University. The hiring process to be used during employee selection is outlined below:
            \subsection Announce job openings via multiple channels (options include Collegian, Marketing, Walla Walla Announcements, Senate emails and the ASWWU Website) at least two weeks before job applications are due.
                \paragraph If an Aswwu employee resigns their job(s), leaves the University, or otherwise vacates their position(s) without two weeks of notice, an interim employee may be hired immediately following the standard hiring process. Other candidates for the position may still apply within the two-week interim period, and if deemed preferable, would replace the interim employee at the end of the two weeks. 
            \subsection Have applicants fill out the job application form available in Appendix A and submit a cover letter, resume, and references as attachments.
            \subsection Applicants shall be interviewed by and at the discretion of the direct supervisor of the position. At the direct supervisor’s discretion, or at the request of the ASWWU President, two additional interviewers may attend the interview. All conclusions regarding each applicant should be documented in writing and submitted to the Executive team.
            \subsection The interviewer(s) should discuss with the Hiring Committee (ASWWU President, ASWWU EVP, and the vice president or department head of the applicable position) to discuss their conclusions regarding each candidate.
            \subsection The Hiring Committee should discuss the interviewers' conclusions and make a hiring decision based on ability, skill level, and the goals of the position.
            \paragraph When applicable, the Hiring Committee’s choice will be taken to the Senate for final approval.
            \subsection The top two (2) candidates may undergo a second interview by the Hiring Committee if necessary.
            \subsection The Financial Vice President, Marketing Vice President, and Atlas Manager shall be hired in accordance with Title 2, Article 1, Sections 7.1, 7.2 and 7.3, respectively, of the ASWWU Bylaws.
            \subsection Deviations from the Hiring Process may be followed with approval from the Hiring Committee and must be announced to the ASWWU Senate in the next regular Senate meeting following the decision to deviate from the process.
                \paragraph Deviations in hiring protocol should be clarified to Senate, explaining which subsections of Section 1, Hiring Practices were not followed and, in compliance with FERPA, giving information on the reasoning behind those deviations. 

        \section[Cyclical Hiring]
        To bring structure and inclusivity to the hiring process, each incoming ASWWU Administration is to follow the hiring process outlined below. The incoming ASWWU Administration is required to follow this procedure to hire a head for each department, and at least 75\% of each department's team by the end of spring quarter of their campaign year.
            \subsection Announce job openings via multiple channels during the last three weeks of winter quarter.
            \subsection Accept applications for Department Head positions during the first two weeks of spring quarter
            \subsection Interview and hire each Department Head during the third and fourth week of spring quarter.
            \subsection Advertise for, and accept employee applications for each department from the first week until the end of the sixth week of spring quarter.
            \subsection Interview and hire employees during the seventh and eighth week of spring quarter
            \subsection Hiring for the positions of Financial Vice President, Marketing Vice President, and Atlas Manager is not subject to this process (see Section 1.7).
            \subsection Deviations from this process may be made with the approval of the Hiring Committee as defined in Section 1.4. 

        \section[Hires Throughout the Year]
        Employees may be hired at other times of the year according to the process outlined in Section 1: Hiring Practices.

        \section[Conflicts of Interest]
        To help ensure objectivity in the process, if a member of the Hiring Committee or an interviewer is a relative or friend of an applicant, he/she should be removed from the hiring process regarding that position. An objective replacement may be sought to temporarily fill the role.

        \section[Personnel Committee Approval]
        The administration must complete the Personnel Committee Hiring Process Checklist and submit it to the Personnel Committee Chair to accompany all personnel legislation.

    \article[Absence Policy]
        \section ASWWU Executive officers and staff are responsible for maintaining regular office/work hours and for attending all required meetings/events. Excessive absenteeism (more than three [3] during the course of the quarter) is grounds for disciplinary action, up to and including termination of employment.
        \section ASWWU Senators must comply with the attendance policy stipulated in Article III, Section 1 of the ASWWU Senate Procedural Rules.
        \section In the case of an emergency absence of a cabinet-level employee, with the exception of the Executive Vice President, the ASWWU President shall appoint a temporary replacement to that position. In the case of subcabinet employees vacating their positions for emergency reasons, their immediate supervisor shall appoint a temporary replacement. This temporary replacement may occupy the vacant position for a term of no longer than five (5) weeks.

    \article[Performance Evaluations]
        \section During the winter quarter, the performance of all ASWWU executive staff, elected positions, and non-elected
        positions will be evaluated. The evaluation process is outlined below:
            \subsection[Executive Positions:]
                \paragraph Every executive position will anonymously evaluate those holding executive positions (including themselves) using the evaluation form available in Appendix B.
                \paragraph The evaluations will be compiled and presented to the ASWWU President.
                \paragraph Each executive position will privately meet with the ASWWU President to discuss their performance to date, go over the evaluations, and establish goals for the next quarter.
                \paragraph Evaluations will be signed and filed in the employees' personnel files.
            \subsection[Senate Positions:]
                \paragraph The ASWWU Executive Vice President will evaluate every senator and the parliamentarian using the evaluation form available in Appendix B.
                \paragraph Every senator and the parliamentarian will anonymously evaluate the EVP using the evaluation form available in Appendix B.
                \paragraph The EVP will meet privately with each senator and the parliamentarian to discuss performance to date, go over the evaluations, and establish goals for the next quarter. 
            \subsection[Non-Elected Positions:]
                \paragraph Supervisor will evaluate each of his/her supervisees using the evaluation form available in Appendix B.
                \paragraph Every ASWWU employee will evaluate his/her personal work performance using the evaluation form available in Appendix B.
                \paragraph Supervisors will privately meet with each employee to discuss his/her performance to date and establish goals for the next quarter.
                \paragraph Evaluations will be signed and filed in the employees' personnel files. 

    \article[Transition Plan]
        \section Due to the nature of ASWWU's annual turnover, it is vital for employees to follow the transition plan outlined below:
            \subsection Maintain up-to-date written/digital documentation regarding job procedures, regular contacts, and other information.
            \subsection Keep all digital documents, correspondence, and planning materials on a computer directory specific to ASWWU. All non-digital documents should be filed in the ASWWU offices.
            \subsection Preceding the deadline for declaring candidacy, all elected officers are required to allocate a minimum of five (5) hours to recruit quality candidates for the elected position they hold. This may involve scheduled events, one-on-one meetings with interested parties, etc. to discuss the duties, expectations, and responsibilities of holding said office.
            \subsection During spring quarter, the incoming officers are required to spend twenty hours in orientation with the existing officers. Training during these twenty hours is to be documented and submitted to the ASWWU President if requested by the President. Orientation hours are meant to:
                \paragraph Provide incoming officers with a better understanding of their positions' responsibilities,
                \paragraph Orient the incoming officers to the locations of documentation and ASWWU procedures,
                \paragraph Introduce incoming officers to key university and community contacts, and
                \paragraph Exchange contact information. 

    \article[Anti-Harassment Policy]
        \section In line with Walla Walla University's Anti-Harassment Policy, the ASWWU seeks to maintain a workplace free of ethnic, racial, religious, or other discriminatory harassment. Physical harassment, slurs, and/or derogatory comments — even in jest — that refer to an individual's race, color, national origin, religion, sex, age, marital status, pregnancy, sexual orientation, handicap, veteran status, or any other classification are inappropriate, unlawful, and will not be tolerated by the ASWWU or by Walla Walla University. This Anti Harassment Policy applies to all ASWWU employees, vendors, contractors, and visitors. Violation of this policy is grounds for disciplinary action, up to and including termination of employment. 
        \section[Sexual Harassment Policy]
            \subsection Sexual harassment, as defined by law, includes any and all unwelcome sexual advances, requests for sexual favors, or any verbal or physical conduct of a sexual nature. Sexual harassment occurs when:
                \paragraph Submission to advances is implicitly or explicitly a term or condition of employment.
                \paragraph Submission or rejection of advances implicitly or explicitly affects employment decisions.
                \paragraph Advances, requests, and/or conduct that interferes with another individual's work performance or creates a hostile/intimidating environment.
            \subsection Examples of sexual harassment include:
                \paragraph Unwanted touching of another employee in an offensive manner.
                \paragraph Implicit or explicit requests for sexual favors.
                \paragraph Continued expression of sexual or social interest after being informed that it is unwelcome.
                \paragraph Graphic or suggestive comments regarding an individual's dress or body.
                \paragraph Verbal comments of a sexual nature.
                \paragraph Degrading an individual through the use of sexual terms or labels.
                \paragraph Displaying sexually offensive objects or pictures in the work environment. 
                \paragraph Making suggestive or insulting noises, obscene gestures, sexual innuendos, or jokes of a sexually specific nature.
        \section The ASWWU will not tolerate sexual harassment or any gender-based conduct that disrupts, harasses, or interferes with employee work performance. Any employee who engages in such harassment is subject to disciplinary action, up to and including termination of employment.
        \section If you are a victim of harassment, you can find support by contacting one of Walla Walla University's deans (Men: x2111; Women: x2531), a counselor at Counseling \& Testing Services (x2147), or the Walla Walla University Church's Christian Counseling Center (x2310).

    \article[Discipline Procedure]
        \section If a member of the ASWWU staff, elected or non-elected, fails to perform the duties outlined for their respective job, the following disciplinary procedure may be followed:
            \subsection[Elected Positions (Executive):]
                \paragraph Removal of elected positions is to be conducted in accordance with Article III, Section 5, or Article IV, Section 3, of the ASWWU Constitution.
                \paragraph When a removal occurs, the Judicial Branch will investigate the case to ensure that the proper procedures were followed.
                \paragraph If three (3) or more Senators believe that the ASWWU President is not addressing an issue, the Executive Vice President can be officially requested to follow the above procedure. Also, if the ASWWU President is not following the duties outlined for his/her position, the Executive Vice President may institute the disciplinary process toward the ASWWU President.
            \subsection[Elected Positions (Legislative):]
                \paragraph If a Senator is absent for three (3) or more Senate meetings in a quarter, that Senator shall be brought before the Senate Executive Committee, who shall decide by a two-thirds vote whether or not the Senator will remain in his/her position.
                \paragraph Portland Campus Senators, if not physically present at Senate meetings, will be considered present if they are included through a conference call from the Portland Campus.
                \paragraph Attendance policies shall be in accordance with Article III, Section 1, of the ASWWU Senate Procedural Rules.
            \subsection[Non-Elected Positions:]
                \paragraph The direct supervisor shall issue a verbal warning, directly identifying the issue and setting a time frame for improvement.
                \paragraph If the time frame is not met or the issue continues, the departmental vice president or the ASWWU President shall issue a written warning instructing specific improvement by a specific date.
                \paragraph Upon lack of improvement, employment will be terminated.
        \section If an individual violates the rules of conduct outlined by the ASWWU governing documents or by Walla Walla University, the ASWWU reserves the right to disregard the disciplinary process and proceed directly with impeachment or recall procedures for elected positions (outlined in Article III, Section 5, and Article IV, Section 3, of the ASWWU Constitution) or termination for non-elected positions. 

    \article[Amendments]
        \section The Personnel Manual may be amended by a two-thirds vote of the Senate.

\title[Job Descriptions]
    \article[Employment Categories]
        \section[Full-Time Positions]
            \subsection Full-time positions must have job descriptions in the Personnel Manual.

        \section[Ad Hoc Positions]
            \subsection Ad Hoc positions have no legislated job description in the Personnel Manual but must follow the ASWWU hiring process.

        \section[Contract Positions]
            \subsection Contract positions are created for specific projects and are exempt from the ASWWU hiring process.
            \subsection Employees in contract positions may work in no more than three (3) consecutive or nonconsecutive calendar weeks per contract within a quarter.
            \subsection In the event that the project extends beyond the contract time period, the ASWWU administration may propose that the contract position transition to an Ad Hoc position. This transition is exempt from the ASWWU hiring process but must still be approved by Senate.
            \subsection There may be no more than three (3) contract employees working concurrently at any time and only twelve (12) contracts per academic year. No individual may be the recipient of more than three (3) contracts per academic year.
            \subsection The ASWWU administration shall send an official letter to the ASWWU Senate informing them of each contract by the next Senate meeting. This letter shall be recorded as an item in the Senate agenda.
            \subsection A contract position may not be used to fill a vacated Ad Hoc position.

    \article[Executive Cabinet]

        \section[President]
            \subsection As the leader of the executive branch of ASWWU, this position is responsible for representing the needs and requests of the student body to Walla Walla University’s administration, faculty, staff, and Board of Trustees. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Perform all presidential duties as outlined in the Bylaws and Constitution.
                    \subparagraph Shadow the current president during spring quarter of the previous year.
                    \subparagraph Outline the vision of the ASWWU administration.
                    \subparagraph Maintain and update the ASWWU five-year strategic plan.
                    \subparagraph Be heavily involved in the planning of the ASWWU CommUnity program each quarter.
                    \subparagraph Review Senate bills, signing those that, in his/her judgment, improve student life and are in agreement with the Constitution and Bylaws and vetoing those that don't.
                    \subparagraph Serve on the hiring committee and recruit and select incoming appointed officers and editors according to the hiring policy outlined in Title I, Article III. Appoint students to Walla Walla University committees requiring student representation within the first five (5) weeks of fall quarter.
                    \subparagraph Appoint students to Walla Walla University committees requiring student representation within the first five (5) weeks of fall quarter.
                    \subparagraph Construct Presidential Annual Report, a comprehensive summary of ASWWU's actions, accomplishments, and goals during their term of office. A physical and electronic copy will be delivered to the Alumni Center, Library archives, and Student Life. Refer to Appendix C for a listing of entities to be included.
                \paragraph[Organization]
                    \subparagraph Maintain up-to-date shared calendar.
                    \subparagraph Maintain regular office hours.
                \paragraph[Communication]
                    \subparagraph Conduct bimonthly meetings with cabinet members and officers.
                    \subparagraph Supervise the ASWWU executive officers, ensuring they perform their duties and meet the performance standards outlined in their respective job descriptions.
                    \subparagraph Chair weekly Cabinet meetings regarding current issues concerning the ASWWU.
                    \subparagraph Communicate biweekly with the Portland ASWWU President.
                    \subparagraph Communicate with the Walla Walla University President regularly.
                    \subparagraph Attend the Walla Walla University Board of Trustees meetings whenever possible.
                    \subparagraph Attend any other committees as per their discretion.
                \paragraph[Finance]
                    \subparagraph Meet with the incoming ASWWU President and Financial Vice President to develop a budget for the upcoming academic year by May 15.
                    \subparagraph Be accountable for the proper use of ASWWU funds.
                    \subparagraph Act as a signee for ASWWU purchases.
            \subsection[Employees]
                \paragraph Hire an Executive Assistant to help with:
                    \subparagraph Agendas
                    \subparagraph Minutes
                    \subparagraph General administrative tasks
                    \subparagraph Communication including email and the office phone
                    \subparagraph Keeping the office clean and stocked
                    \subparagraph Assistance in planning events that the ASWWU President is responsible for
                    \subparagraph Assistance with other administrative tasks

            \subsection[Basic knowledge]
                \paragraph Basic knowledge of the ASWWU governing documents.
                \paragraph Working knowledge of Robert's Rules of Order.

            \subsection[Emergency Succession]
                \paragraph In the event that the President is impeached, removed from office, dies or resigns the EVP will assume the position of ASWWU President. 

        \section[Executive Vice President (EVP)]
            \subsection As a member of the executive branch of the ASWWU, this position is responsible for communicating the needs and requests of the student body to Walla Walla University's administration, faculty, and staff. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Sign all bills passed by Senate to verify authenticity and compliance with the ASWWU Constitution and Bylaws.
                    \subparagraph Assist Senate in solving problems that arise.
                    \subparagraph Serve as Election Board Chair, organizing and monitoring the election according to the procedures outlined in the Elections Manual.
                    \subparagraph Chair weekly Senate meetings in accordance with the Constitution and Bylaws.
                    \subparagraph Promote student involvement in Senate.
                    \subparagraph Require Senators to contact their constituents regularly and monitor contact via a reporting process.
                    \subparagraph In the event that the President is impeached, removed from office, dies or resigns the EVP will assume the position of ASWWU President.
                    \subparagraph Oversee that all Senate Committees are diligent about their responsibilities.
                    \subparagraph Monitor the ASWWU President's performance standards outlined in the job description.
                    \subparagraph Represent the ASWWU if the President is unable to perform their duties due to absence or illness.
                    \subparagraph In the event that the President is impeached, removed from office, dies or resigns the EVP will assume the position of ASWWU President.
                \paragraph[Organization]
                    \subparagraph Maintain regular office hours.
                    \subparagraph Maintain an up-to-date shared calendar.
                \paragraph[Communication]
                    \subparagraph Check with other Executive Officers on a weekly basis and assist them as needed.
                    \subparagraph Communicate with the Walla Walla University administration on a weekly basis.
                    \subparagraph Serve on the Walla Walla University Faculty Senate. 
                    \subparagraph Attend any other committee as per his/her discretion or request by the President or Senate.
                \paragraph[Finance]
                    \subparagraph Monitor the Senate's budget, ensuring that it is kept on target.
                    \subparagraph Supervise Senators and Senate staff payroll.
                    \subparagraph Account for the expenses of Senators’ district allowances.
                    \subparagraph Act as a signee for ASWWU purchases.
            \subsection[Employees]
                \paragraph Hire an assistant (AEVP) to help with:
                    \subparagraph Preparing for Senate
                        \subsubparagraph Keeping track of all Bills that are on the table
                        \subsubparagraph Preparing accurate PowerPoints
                        \subsubparagraph Contacting the Portland Senators
                    \subparagraph Communicating with Senators
                    \subparagraph Maintaining the ASWWU Digital Senate Archive
                    \subparagraph Helping Senate sessions run smoothly
                    \subparagraph Other miscellaneous duties
                \paragraph[Senate Secretary]
                    \subparagraph Take minutes during Senate meetings
                    \subparagraph Take minutes during other miscellaneous meetings as necessary
                    \subparagraph Share the minutes with the senators in a timely manner
                    \subparagraph Implementing any amendment to the minutes before they are approved by the senate
            \subsection[Basic Knowledge]
                \paragraph In-depth knowledge of the ASWWU governing documents.
                \paragraph In-depth knowledge of Robert's Rules of Order.
            \subsection[Pro-Tempore and Successions]
                \paragraph A pro-tempore will be nominated from the Senate body as outlined in the Senate Procedural Rules to maintain the responsibilities of the Executive Vice President in the event of the incumbent's temporary leave of absence; or to succeed him/her in the event that the EVP is impeached, removed from office, dies or resigns.

        \section[Financial Vice President (FVP)]
            \subsection As a member of the executive branch of the ASWWU, this position is responsible for maintaining the financial health of the ASWWU. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Conduct annual budget workshop for incoming officers.
                    \subparagraph Workshop should include:
                        \subsubparagraph Departmental budget development process,
                        \subsubparagraph Proper spending procedures, and
                        \subsubparagraph Common financial issues faced during the year and possible solutions.
                    \subparagraph Meet regularly with the President to keep them up to date on ASWWU's financial matters.
                    \subparagraph Advise and monitor ASWWU Cabinet and department heads on financial matters.
                    \subparagraph Prepare weekly, quarterly, and yearly financial reports for ASWWU Cabinet members and department heads.
                    \subparagraph Hire all ASWWU employees and maintain hiring records.
                    \subparagraph Approve employee timecards every pay period.
                    \subparagraph Prepare monthly credit card statements for the WWU Accounting department.
                    \subparagraph Prepare checks and reimbursements.
                    \subparagraph Maintain financial records with Intuit QuickBooks.
                    \subparagraph Complete other duties as assigned or as necessary.
                \paragraph[Organization]
                    \subparagraph Maintain regular office hours.
                    \subparagraph Maintain detailed record of income and expenses; make sure accounts balance at the end of each work session. 
                    \subparagraph Maintain up-to-date shared calendar.
                \paragraph[Communication]
                    \subparagraph Communicate with the ASWWU departments on a weekly basis, ensuring financial data is kept current.
                    \subparagraph Set up and maintain regular meetings with Walla Walla University's accounting department.
                    \subparagraph Address issues of departments exceeding their budget within three (3) business days of its occurrence.
                \paragraph[Finance]
                    \subparagraph Monitor ASWWU's expenditures, including but not limited to:
                        \subsubparagraph Approving and recording reimbursements within five (5) work days of the request.
                        \subsubparagraph Approving, submitting, and recording all orders and invoices within five (5) work days of receipt.
                        \subsubparagraph Monitoring and recording use of petty cash, prize money, etc.
                        \subsubparagraph Acting as a signee for ASWWU purchases.
                        \subsubparagraph Meeting with the chairperson of Senate's Finance Committee regularly to review ASWWU purchases as stipulated in Title 3 of the ASWWU Bylaws.
                    \subparagraph Develop and monitor the ASWWU budget, including but not limited to:
                        \subsubparagraph Assisting Executive Officers in developing departmental budgets.
                        \subsubparagraph Approving and monitoring departmental budgets.
                        \subsubparagraph Maintaining accurate, up-to-date records of ASWWU expenditures that are accessible to all ASWWU members.
                        \subsubparagraph Prepare weekly financial reports for cabinet members. Reports should address:
                            \subsubsubparagraph Budget year-to-date.
                            \subsubsubparagraph Any concerns regarding budgets.
            \subsection[Employees]
                \paragraph Hire an ASWWU Controller to assist with FVP duties. The Controller's job description is listed in the Executive Assistants Article this Title.
                \paragraph Directly oversee and meet regularly with the following department heads:
                    \subparagraph Atlas Manager
                    \subparagraph Global Service Director
                    \subparagraph Tread Shed Manager
                    \subparagraph Outdoors Head
            \subsection[Basic Knowledge]
                \paragraph In-depth knowledge of the ASWWU governing documents.
                \paragraph Working knowledge of Robert's Rules of Order.
            \subsection[Technical Skills]
                \paragraph Intermediate to advanced knowledge of Microsoft Excel.
                \paragraph Proficient with Microsoft Office Suite.
                \paragraph Proficiency in Intuit QuickBooks.
                \paragraph Completion of Principles of Accounting course series (ACCT 201-203) or equivalent. 

        \section[Portland Vice President (PVP)]
            \subsection As a member of the executive branch of the ASWWU, this position is responsible for communicating Portland campus's needs and requests to the ASWWU's College Place constituents and leaders as well as planning and implementing programs on the Portland Campus. This position of service pursues changes that will improve the quality of student life on the Portland campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Coordinate monthly ASWWU meeting on the Portland campus.
                    \subparagraph Organize monthly social activities.
                \paragraph[Organization]
                    \subparagraph Maintain regular office hours.
                \paragraph[Communication]
                    \subparagraph Promote Portland ASWWU meetings and activities to students via multiple channels for one (1) week prior to the meeting or activity.
                    \subparagraph Advertise specific College Place campus events on the Portland campus.
                    \subparagraph Communicate with the ASWWU President on a weekly basis.
                \paragraph[Finance]
                    \subparagraph Approve all Portland ASWWU expenditures in conjunction with Portland Advisor.
                    \subparagraph Work with the Financial Vice President to develop a budget for the year and to control costs.
                    \subparagraph Monitor expenditures to ensure that they are within the budget.
                    \subparagraph Submit receipts for expenditures to the School of Nursing office manager within five (5) working days of purchase.
            \subsection[Basic Knowledge]
                \paragraph In-depth knowledge of the ASWWU governing documents.
                \paragraph Working knowledge of \textit{Robert's Rules of Order}.
            \subsection[Technical Skills]
                \paragraph Proficient with Microsoft Office Suite. 

        \section[Spiritual Vice President (SVP)]
            \subsection As a member of the executive branch of the ASWWU, this position is responsible for developing and implementing programs that meet the spiritual needs of the student body. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Choose speakers for Student Week of Prayer, manage the schedule for the week, and assist with preparation as needed.
                    \subparagraph Organize afternoon retreat for Student Week of Prayer speakers.
                    \subparagraph Provide additional religious events, such as religious concerts, inspirational speakers, etc.
                    \subparagraph Maintain a good relationship with Campus Ministries.
                    \subparagraph Keep electronic records of events and planning.
                \paragraph[Organization]
                    \subparagraph Maintain regular office hours.
                    \subparagraph Maintain a campus-wide, up-to-date calendar on a service such as Basecamp or Outlook.
                \paragraph[Communication]
                    \subparagraph Coordinate with Social Vice President as necessary.
                    \subparagraph Work with Marketing VP and The Collegian Editor-in-Chief to promote activities on campus and throughout the community.
                    \subparagraph Maintain periodical contact with Walla Walla University spiritual leaders, including but not limited to the:
                        \subsubparagraph Campus Chaplain,
                        \subsubparagraph University Church pastoral staff, and
                        \subsubparagraph Student ministry leaders (Heubach Worship, Berean Fellowship, Hispanic Ministries etc.).
                \paragraph[Finance]
                    \subparagraph Work with the Financial Vice President to develop a budget for the year.
                    \subparagraph Monitor expenditures to ensure that they are within the budget.
                    \subparagraph Submit receipts for expenditures to the Financial Vice President within five (5) working days of purchase.
            \subsection[Employees]
                \paragraph Hire a sufficient number of team members in accordance with the hiring procedure outlined in Title I.
                \paragraph Hold regular team meetings.
                \paragraph Monitor team performance.
            \subsection[Basic Knowledge]
                \paragraph In-depth knowledge of the Seventh-day Adventist belief system.
                \paragraph General knowledge of the ASWWU governing documents. 

        \section[Social Vice President (SoVP)]
            \subsection As a member of the executive branch of the ASWWU, this position is responsible for developing and implementing social programs for the student body. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Plan and implement ideas for the Barn Party, Spring Jam, Battle of the Bands, and Banquets(s).
                    \subparagraph Provide Review Week activities.
                    \subparagraph Invite various club presidents and university departments to collaborate with ASWWU Social on events and projects.
                \paragraph[Organization]
                    \subparagraph Maintain regular office hours.
                    \subparagraph Maintain a campus-wide, up-to-date calendar on a service such as Basecamp or Outlook.
                \paragraph[Communication]
                    \subparagraph Work with Marketing VP and Collegian Editor-in-Chief to promote activities on campus and throughout the community.
                    \subparagraph Maintain regular contact with Walla Walla University's Student Activities Director.
                \paragraph[Finance]
                    \subparagraph Work with the Financial Vice President to develop a budget for the year.
                    \subparagraph Verify timecards for departmental staff.
                    \subparagraph Monitor expenditures to ensure that they are within the budget.
                    \subparagraph Submit receipts for expenditures to the Financial Vice President within five (5) working days of purchase.
            \subsection[Employees]
                \paragraph Hire a sufficient number of team members in accordance with the hiring procedure outlined in Title 1.
                \paragraph Hold regular team meetings.
                \paragraph Monitor team performance.
            \subsection[Knowledge]
                \paragraph Basic knowledge of ASWWU's governing documents.
                \paragraph Basic knowledge of \textit{Robert's Rules of Order}.

        \section[Marketing Vice President]
            \subsection As a member of the executive branch of the ASWWU, this position is responsible for communicating the ASWWU's activities and mission to its members and ensuring the consistency and clarity of that communication. This position of service improves the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Advertise events via various media and communication channels.
                    \subparagraph Oversee Marketing Department staff hiring, assignment delegations, and progress evaluations.
                    \subparagraph Maintain knowledge of all ASWWU events and coordinate communication of those events to the ASWWU members.
                    \subparagraph Represent the media department heads in ASWWU Cabinet.
                    \subparagraph Approve media/advertising materials and programs in accordance with the standards of the ASWWU and the Vice President of Student Administration.
                    \subparagraph Oversee the design, purchasing, and distribution of any campus-wide shirts and sweatshirts.
                    \subparagraph Ensure that shirt/sweatshirt purchasing (as outlined above) is inclusive of the student body. Recommended 1 percent minimum of purchase for XS, 2XL, 3XL/3XLT, and 4XL/4XLT, respectivley.
                \paragraph[Organization]
                    \subparagraph Maintain up-to-date shared calendar.
                    \subparagraph Check and correspond via email regularly.
                    \subparagraph Maintain regular office hours.
                \paragraph[Communication]
                    \subparagraph[Campus Relations]
                        \subsubparagraph Communicate functions of the ASWWU to its members. 
                        \subsubparagraph Facilitate creation and implementation of the following forms of mass communication:
                            \subsubsubparagraph Posters
                            \subsubsubparagraph Website(s)
                            \subsubsubparagraph Community Center Announcements
                            \subsubsubparagraph Outgoing ASWWU Mass Email
                            \subsubsubparagraph Collegian Ads
                            \subsubsubparagraph Videos
                            \subsubsubparagraph CommUnity PowerPoints
                            \subsubsubparagraph CommUnity Announcements
                            \subsubsubparagraph ASWWU Social Media Pages
                            \subsubsubparagraph Text Messages
                    \subparagraph[Internal Relations]
                        \subsubparagraph Work with designers to complete special design projects (e.g., recycling campaign, Tread Shed bike signs, etc.).
                        \subsubparagraph Liaison between cabinet members and external campus leaders by
                            \subsubsubparagraph Attending weekly cabinet and officer meetings.
                            \subsubsubparagraph Coordinating schedule and event details.
                            \subsubsubparagraph Communicating with Collegian, AGA, OPS, Village Life, MES/University Relations staff and various other campus organizations.
                \paragraph[Finance]
                    \subparagraph Monitor Marketing Department expenditures to ensure they are within budget.
                    \subparagraph Process invoices from ASWWU contract employees.
            \subsection[Employees]
                \paragraph Hire a Marketing team consisting of Assistants and Designers to assist with marketing responsibilities.
                \paragraph Hold regular Marketing team meetings.
                \paragraph Monitor team performance.
                \paragraph Directly oversee and meet regularly with the following department heads:
                    \subparagraph Mountain Ash Editor
                    \subparagraph Webmaster
                    \subparagraph Photo Head
                    \subparagraph Video Director
            \subsection[Knowledge]
                \paragraph Basic knowledge of the ASWWU governing documents.
                \paragraph Basic understanding of Robert's Rules of Order.
                \paragraph Recommended design and marketing experience.*
            \subsection[Recommended Technical Skills]
                \paragraph Microsoft Office Suite.
                \paragraph Typo3.
                \paragraph Adobe InDesign.*
                \paragraph Adobe Photoshop.*

        \section[Diversity and Wellness Officer]
            \subsection As a member of the executive branch of ASWWU, this posistion is responsible for communicating various perspectives of the student body to the ASWWU Cabinet, Walla Walla University's administration, and Diversity, Equity, and Inclusion (DEI) committees. This posistion of service pursues changes that will impove the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Create and chair a monthly ASWWU Diversity and Inclusion Committee in accordance to the Bylaws
                    \subparagraph Attend monthly WWU Diversity and Inclusion Council meetings.
                    \subparagraph Attend monthly Donald Blake Center Council meetings.
                    \subparagraph Attend weekly Haven meetings (also strongly encouraged attendance of University Pride weekly meetings).
                    \subparagraph Monitor that ASWWU events are being well received and inclusive of the student body.
                    \subparagraph Promote wellness and cultural events put on by other organizations and clubs on campus.
                    \subparagraph Coordinate collaborative educational opportuniteis for the student body (such as with the Donald Blake Center or Student Health and Wellness).
                \paragraph[Organization]
                    \subparagraph Maintain regular office hours.
                    \subparagraph Maintain an up-to-date shared calendar.
                \paragraph[Communication]
                    \subparagraph Meet with the Social VP, the Spiritual VP, and other department heads as necessary at the beginning of each quarter to review their respective planned events for that quarter.
                    \subparagraph Communicate with the ASWWU President on a biweekly basis.
                    \subparagraph Attend weekly Cabinet meetings.
                    \subparagraph Work with Marketing VP and Collegian Editor-in-Chief to promote collaborative events between ASWWU and other campus organizations.
                    \subparagraph Communicate with the carious councils and committees as needed.
                \paragraph[Finance]
                    \subparagraph Work with Financial VP to develop a budget for the year.
                    \subparagraph Monitor expenditures to ensure that they are within the budget.
                    \subparagraph Submit receipts for expenditures to ensure that they are within the budget.
                \paragraph[Knowledge]
                    \subparagraph Basic knowledge of ASWWU's governing documents.
                    \subparagraph Awareness and involvement with various student groups on campus.
                    
        \section[Portland Financial Vice President (PFVP)]
            \subsection As a member of the executive branch of the ASWWU, this position is responsible for maintaining the financial health of the Portland branch of the ASWWU. This position of service pursues changes that will improve the quality of student life on the Portland campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Conduct annual budget planning for incoming Portland officers.
                    \subparagraph Panning should include:
                        \subsubparagraph Departmental budget development process.
                        \subsubparagraph Proper spending procedures.
                        \subsubparagraph Common financial issues faced during the year and possible solutions. 
                \paragraph[Organization]
                    \subparagraph Maintain regular office hours.
                    \subparagraph Maintain detailed record of income and expenses; make sure accounts balance at the end of each work session.
                \paragraph[People]
                    \subparagraph Advise the Portland ASWWU officers on financial matters.
                \paragraph[Communication]
                    \subparagraph Communicate with Portland's ASWWU officers on a regular basis, ensuring financial data is kept current.
                    \subparagraph Set up and maintain monthly meetings with ASWWU's Financial Vice President at the College Place campus.
                    \subparagraph Address issues of officers exceeding their budget within three (3) business days of the occurrence.
                \paragraph[Finance]
                    \subparagraph Monitor Portland’s ASWWU expenditures, including but not limited to:
                        \subsubparagraph Approve and record reimbursements within five (5) work days of request.
                        \subsubparagraph Approve, submit, and record all orders and invoices within five (5) work days of receipt.
                        \subsubparagraph Monitor and record use of petty cash, prize money, etc.
                        \subsubparagraph Act as a signee for Portland's ASWWU purchases.
                    \subparagraph Develop and monitor Portland's ASWWU budget, including but not limited to:
                        \subsubparagraph Assist officers in developing the budget.
                        \subsubparagraph Maintain accurate, up-to-date records of Portland's ASWWU expenditures that are accessible to all ASWWU members.
                        \subsubparagraph Prepare monthly financial reports to the Financial Vice President at the College Place campus. Reports should address:
                            \subsubsubparagraph Budget year-to-date.
                            \subsubsubparagraph Any concerns regarding budget.
            \subsection[Basic Knowledge]
                \paragraph In-depth knowledge of the ASWWU governing documents.
                \paragraph Working knowledge of Robert's Rules of Order.
            \subsection[Technical Skills]
                \paragraph Working knowledge of Microsoft Excel.
                \paragraph Proficient with Microsoft Office Suite.
                \paragraph Accounting proficiency. 

        \section[Atlas Staff]
            \subsection[General]
                \paragraph[Basic Requirements]
                    \subparagraph Knowledge of office operations and equipment.
                    \subparagraph Proficient with Microsoft Office Suite.
                    \subparagraph Food worker card.
                \paragraph[Employment]
                    \subparagraph Shifts will last from two to four (2-4) hours in duration, not exceeding two (2) shifts per day.
                    \subparagraph An employee may work a maximum of sixteen (16) hours per week (or a lesser amount if total student employment would exceed standards accepted by WWU for an enrolled full/part-time student). Please see the WWU student handbook for details.
            \subsection[Atlas Manager]
                \paragraph The Atlas Manager is responsible for supervising activity within the Atlas, managing regular operations, communicating regular updates to the ASWWU Cabinet, and creating both short- and long-term strategic plans for The Atlas.
                \paragraph The Atlas Manager will be appointed after an application and interview process. It is strongly recommended that the Atlas Manager be selected from applicants who have at least one (1) school year experience as an Atlas Assistant Manager or Atlas Barista. 
                \paragraph[Responsibilities]
                    \subparagraph[Duties]
                        \subsubparagraph Operate Atlas daily business.
                        \subsubparagraph Oversee student employees, facilities management, inventory status, and other duties not listed herein.
                        \subsubparagraph Select and propose candidates for employment at The Atlas to the ASWWU administration.
                        \subsubparagraph Maintain financial records of daily transactions, weekly revenues, monthly budgets, etc.
                        \subsubparagraph Work with Social Vice President and/or Student Activities Director to assist with social activities in The Atlas.
                    \subparagraph[Organization]
                        \subsubparagraph Set normal operating hours based on services rendered. Hours of operation are contingent upon review by ASWWU administration and approval by WWU Administration.
                        \subsubparagraph Maintain an event calendar on as.wallawalla.edu.
                        \subsubparagraph Manage scheduling for third-party events (on-campus clubs, open mic nights, post-fireside, etc.).
                        \subsubparagraph Delegate management tasks during day-to-day operation to cover Atlas manager's absence caused by classes, club trips, and/or other academic conflicts.
                    \subparagraph[Communication]
                        \subsubparagraph Provide reports to the President and FVP on a weekly/monthly basis (reports to be determined).
                        \subsubparagraph Work with the FVP (or Controller) for supply ordering and payroll.
                        \subsubparagraph Coordinate with the Marketing Vice President to develop promotional materials to advertise events and products.
                    \subparagraph[Finance]
                        \subsubparagraph Work with the Financial Vice President to establish a working budget.
                        \subsubparagraph Monitor expenditures to ensure that they are within the budget.
                        \subsubparagraph Submit receipts for expenditures to the FVP within five (5) business days of purchase.
                        \subsubparagraph Obtain clearance for all expenditures greater than \$500 (including regularly scheduled inventory purchases) and for all capital expenditures regardless of value.
                    \subparagraph[Education]
                        \subsubparagraph Successful completion of a management class (concurrent enrollment does not fulfill this requirement).
                        \subsubparagraph Successful completion of a basic accounting series (concurrent enrollment does not fulfill this requirement). 

            \subsection[Atlas Assistant Manager]
                \paragraph The Atlas Manager has the ability to hire (an) assistant manager(s).
                \paragraph[Responsibilities]
                    \subparagraph[Duties]
                        \subsubparagraph Operate Atlas daily business.
                        \subsubparagraph Maintain a clean environment conducive to studying and enjoyable student visits.
                        \subsubparagraph Oversee customer satisfaction, facilities management, basic cleaning and maintenance, opening for business, closing at the end of the day, and other duties not listed herein.
                        \subsubparagraph Prepare and balance the till at the start and end of each shift.
                        \subsubparagraph Assist during social activities hosted at The Atlas.
                        \subsubparagraph Monitor multimedia use in accordance within the guidelines and limits of Walla Walla University.
                    \subparagraph[Organization]
                        \subsubparagraph Maintain normal operating hours.
                        \subsubparagraph Maintain an event calendar on as.wallawalla.edu.
                        \subsubparagraph Assist in scheduling for third-party events.
                    \subparagraph[People]
                        \subsubparagraph Work with the Atlas Manager on inventory, scheduling, purchasing, and longterm planning.
                    \subparagraph[Communication]
                        \subsubparagraph Update reports used to communicate with the President and FVP on a daily basis (reports to be determined).
                        \subsubparagraph Ensure customer satisfaction by taking a proactive role with customers.
                    \subparagraph[Finance]
                        \subsubparagraph Monitor expenditures to ensure that they are within the budget.
                        \subsubparagraph Submit receipts for expenditures to the FVP within five (5) work days of purchase.
                    \subparagraph[Education]
                        \subsubparagraph Concurrent enrollment or successful completion of a management class is recommended.
                        \subsubparagraph Concurrent enrollment or successful completion of a basic accounting series is recommended.
            \subsection[Atlas Barista]
                \paragraph This position is responsible for maintaining The Atlas by making drinks and keeping The Atlas running smoothly. This position also requires a high level of professionalism and friendliness. This position of service improves the quality of student life on campus. A number of students will be employed as Atlas Baristas, the number to be determined at the discretion of ASWWU administration in conjunction with the Atlas Manager
                \paragraph[Responsibilities]
                    \subparagraph[Duties]
                        \subsubparagraph Operate Atlas daily business.
                        \subsubparagraph Fulfill and execute all procedures laid out by Atlas Manager and quality control specialist.
                        \subsubparagraph Maintain a clean environment conducive to studying and enjoyable student visits.
                        \subsubparagraph Oversee customer satisfaction, facilities management, basic cleaning and maintenance, opening for business, closing at the end of the day, and other duties not listed herein.
                        \subsubparagraph Assist during social activities hosted at The Atlas.
                        \subsubparagraph Monitor multimedia use in accordance within the guidelines and limits of Walla Walla University.
                        \subsubparagraph At times responsible for aiding in the development of new/seasonal drinks.
                    \subparagraph[People]
                        \subsubparagraph Work with the Atlas Manager on inventory and scheduling.
                        \subsubparagraph Maintain scheduled work hours.
                        \subsubparagraph Attend weekly barista meetings.
                        \subsubparagraph Work with other baristas.
                    \subparagraph[Communication]
                        \subsubparagraph Ensure customer satisfaction by taking a proactive role with customers.
                    \subparagraph[Finance]
                        \subsubparagraph Each barista is responsible for maintaining an accurate till. The employee may be held personally responsible for missing funds.
                        \subsubparagraph Prepare the till before each shift.
                        \subsubparagraph Tally and report till balance at the end of each shift.
                \paragraph[Technical Skills]
                    \subparagraph Must obtain a food worker card. 
                    \subparagraph Prior barista experience highly recommended but not required (can be trained in). 

    \article[Executive Officers]

        \section[Administrative Assistant]
            \subsection As an assistant to a leader of the executive branch of the ASWWU, this position is responsible for assisting the members of the cabinet represent the needs and requests of the student body to Walla Walla University's administration, faculty, and staff.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Perform tasks as assigned by (a) supervising cabinet member(s).
                \paragraph[Organization]
                    \subparagraph Maintain regular office hours.
                    \subparagraph Clean office and file papers in appropriate locations.
                    \subparagraph Maintain up-to-date shared calendar.
                \paragraph[People]
                    \subparagraph Listen to the concerns of students and communicate them to the President and other Executive Officers as appropriate.
                \paragraph[Communication]
                    \subparagraph Meet weekly with the supervising cabinet member(s) to discuss their schedule(s), determine needs, and develop a to-do list.
                    \subparagraph Monitor department activity and progress.
                \paragraph[Finance]
                    \subparagraph Purchase office supplies as requested.
                    \subparagraph Monitor expenditures to ensure that they are within the budget.
                    \subparagraph Submit receipts for expenditures to the Financial Vice President within five (5) work days of purchase.
            \subsection[Basic Knowledge]
                \paragraph Basic knowledge of ASWWU's governing documents.
                \paragraph Knowledge of basic office operations and equipment.
            \subsection[Technical Skills]
                \paragraph Proficient with Microsoft Office Suite.

        \section[\textit{The Collegian} Editor-in-Chief]
            \subsection This position is responsible for producing a quality student paper that represents Walla Walla University's student body and upholds the standards of Walla Walla University. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Plan, organize, publish, and ensure the distribution of \textit{The Collegian} on a weekly basis (no fewer than 26 per school year).
                        \subsubparagraph Work with Head Layout Editor to develop an encompassing theme and design for \textit{The Collegian}.
                        \subsubparagraph Develop a weekly production timeline.
                        \subsubparagraph Assist staff in acquiring articles and material for each section.
                        \subsubparagraph Stay in contact with the Portland campus librarian, academic departments, and the administration on a weekly basis to gather campus news.
                        \subsubparagraph Ensure that \textit{The Collegian} is distributed at both the College Place and Portland campuses.
                        \subsubparagraph Ensure the E.L. Mabley Archives is given two (2) copies of each \textit{Collegian} issue, both in physical and electronic formats.
                        \subsubparagraph Bind two (2) copies of the full volume of \textit{The Collegian} in order to preserve and maintain the ASWWU Archives.
                        \subsubparagraph Bind the year's volume of \textit{The Collegian} and distribute a copy to each staff member.
                    \subparagraph Adhere to the Society of Professional Journalists Code of Ethics. 
                    \subparagraph Provide a professional, engaging, and constructive work environment.
                    \subparagraph Conduct a weekly editorial board meeting that includes a WWU staff member to approve content.
                    \subparagraph Lead out during \textit{Collegian} night.
                \paragraph[Organization]
                    \subparagraph Maintain up-to-date shared calendar.
                    \subparagraph Maintain regular office hours.
                    \subparagraph Revise and maintain \textit{The Collegian's} contributing writer policy.
                \paragraph[Communication]
                    \subparagraph Internal Relations
                        \subsubparagraph Coordinate with the ASWWU Marketing Vice President and other media department heads regarding equipment requests.
                        \subsubparagraph Meet with Marketing Vice President to discuss advertising rates, dimensions, and packages.
                        \subsubparagraph Work with Financial Vice President to develop a budget for the upcoming year.
                        \subsubparagraph Hold weekly staff meetings to discuss progress, address issues, and determine goals.
                        \subsubparagraph Communicate progress and issues to the ASWWU Marketing Vice President and the Media Board on a weekly basis.
                        \subsubparagraph Consult with the Collegian advisor and ASWWU President on a weekly basis.
                        \subsubparagraph Conduct quarterly reviews of section editors and give feedback that will foster improvement.
                    \subparagraph[External Relations]
                        \subsubparagraph Work with the \textit{Collegian} publisher in a timely, responsible, and professional manner.
                        \subsubparagraph Establish and have monthly meetings with a faculty or community member that works in the design/publication field
                \paragraph[Finance]
                    \subparagraph Monitor expenditures to ensure that they are within \textit{The Collegian's} budget.
                    \subparagraph Submit receipts for expenditures to the Financial Vice President within five (5) work days of purchase.
                    \subparagraph Verify timecards for \textit{Collegian} staff.
                    \subparagraph Calculate each contributing writer's word count and verify that they get paid.
            \subsection[Employees]
                \paragraph Hire a team to take on the following responsibilities:
                    \subparagraph[Assistant Editor]
                        \subsubparagraph Maintain a weekly calendar
                        \subsubparagraph Write when called upon
                        \subsubparagraph Check in with staff members
                        \subsubparagraph Take on miscellaneous projects
                        \subsubparagraph Engage in Editorial Board
                        \subsubparagraph Be involved during \textit{Collegian} night
                    \subparagraph[Head Layout Editor]
                        \subsubparagraph Develop overall theme for \textit{The Collegian}
                        \subsubparagraph Create a high quality and relevant cover each week
                        \subsubparagraph Supervise layout editors
                    \subparagraph[Head Copy Editor]
                        \subsubparagraph Use the PA Manual of style as a guide to create standards for headlines, abbreviations, etc.
                        \subsubparagraph Supervise and assign articles to copy editors for proofreading.
                        \subsubparagraph Read and sign off on each page of \textit{The Collegian} before it is ready to print.
            \subsection[Basic Knowledge]
                \paragraph Basic knowledge of ASWWU's governing documents.
                \paragraph Understand the principles of journalism. 
            \subsection[Technical Skills]
                \paragraph Adobe InDesign.*
                \paragraph Adobe Photoshop.*
                \paragraph Mac OS.
                \paragraph Microsoft Windows.
                \paragraph Proficient with Microsoft Office Suite.

        \section[ASWWU Chief of Staff]
            \subsection This position is responsible for taking minutes at ASWWU meetings and working with the Administrative Assistants to help ASWWU pursue changes that will improve student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Obtain, sort, and deliver mail daily.
                    \subparagraph Schedule meetings and track attendance.
                    \subparagraph Take detailed, legible minutes at meetings including but not limited to:
                        \subsubparagraph Executive Cabinet meetings.
                        \subsubparagraph Media Board meetings.
                        \subsubparagraph Judiciary Hearings.
                    \subparagraph Transcribe, print, and hole punch meeting minutes, agendas, and other documents as directed by the President at each ASWWU Executive meeting.
                    \subparagraph Work on special projects as assigned by the ASWWU President.
                    \subparagraph Support the different ASWWU departments by providing additional secretarial work.
                \paragraph[Organization]
                    \subparagraph Maintain regular office hours.
                    \subparagraph Clean ASWWU's main office and file papers in appropriate locations.
                    \subparagraph Maintain a campus-wide, up-to-date calendar.
                \paragraph[Communication]
                    \subparagraph Contact committee members when a meeting is canceled or changed.
                    \subparagraph Listen to the concerns of students and communicate them to the President and other Executive Officers as appropriate.
                \paragraph[Basic Knowledge]
                    \subparagraph Basic knowledge of ASWWU's governing documents.
                    \subparagraph Knowledge of basic office operations and equipment.
                \paragraph[Technical Skills]
                    \subparagraph Proficient with Microsoft Office Suite.
                    \subparagraph Proper minutes formatting. 

        \section[\textit{Mask} Editor]
            \subsection This position is responsible for producing the printed and online version of the Mask, representing Walla Walla University’s student body, and upholding the standards of Walla Walla University.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Deliver a final proof of the Mask to Color Press or another printing facility by the end of the fifth week of fall quarter.
                        \subsubparagraph Facilitate a Portland campus photographer.
                        \subsubparagraph Coordinate with Walla Walla University's mail room to distribute Masks to faculty, staff, and Portland students.
                    \subparagraph Provide a complete, online mask within one (1) week of photo completion. The online Mask should include:
                        \subsubparagraph Advanced search options.
                        \subsubparagraph Mask archives.
                        \subsubparagraph Login capabilities.
                        \subsubparagraph Control over levels of access to personal information.
                        \subsubparagraph Comply with the Media Board Manual.
                \paragraph[Organization]
                    \subparagraph Develop a production timeline. 
                    \subparagraph Delegate tasks to Mask staff members.
                    \subparagraph Maintain regular office hours.
                    \subparagraph Maintain an up-to-date calendar.
                \paragraph[People]
                    \subparagraph Nominate Mask staff to the ASWWU President.
                    \subparagraph Supervise Mask staff, ensuring diligence and quality work.
                    \subparagraph Evaluate staff performance on a quarterly.
                    \subparagraph Coordinate with the ASWWU Marketing Vice President, the \textit{Mountain Ash} editor, \textit{Collegian} editor, and the ASWWU Systems Manager regarding equipment requests.
                \paragraph[Communication]
                    \subparagraph Meet with Marketing Vice President to discuss advertising rates, dimensions, and packages.
                    \subparagraph Hold weekly Mask staff meetings to discuss progress, address issues, and determine goals.
                    \subparagraph Communicate progress and issues to the ASWWU Marketing Vice President and the Media Board.
                    \subparagraph Coordinate with Student Administration regarding content approval.
                    \subparagraph Publicize Mask photo schedules and information deadlines to the public through multiple media two (2) weeks prior to deadline.
                \paragraph[Finance]
                    \subparagraph Work with the Financial Vice President to develop a budget for the year.
                    \subparagraph Monitor expenditures to ensure that they are within the budget.
                    \subparagraph Submit receipts for expenditures to the Financial Vice President within five (5) work days of purchase.
                    \subparagraph Verify timecards for Mask staff.
                    \subparagraph Calculate and set price of Masks for purchase.
            \subsection[Basic Knowledge]
                \paragraph Basic knowledge of ASWWU's governing documents.
                \paragraph Expertise in design principles.
                \paragraph Basic knowledge of computer coding.
            \subsection[Technical Skills]
                \paragraph Full knowledge of Adobe InDesign.
                \paragraph Full knowledge of Adobe Photoshop.
                \paragraph Full knowledge of Adobe Illustrator.

        \section[\textit{Mountain Ash} Editor]
            \subsection This position is responsible for producing a quality yearbook that represents Walla Walla University's student body and upholds the standard of Walla Walla University.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Plan, organize, publish, and distribute the Mountain Ash before finals week of spring quarter.
                    \subparagraph Comply with the Media Board Manual.
                    \subparagraph Ensure that steps are taken to represent the whole student body in the Mountain Ash.
                \paragraph[Organization]
                    \subparagraph Develop a production timeline.
                    \subparagraph Delegate tasks to Mountain Ash staff members.
                    \subparagraph Maintain regular office hours.
                    \subparagraph Maintain up-to-date shared calendar.
                \paragraph[People]
                    \subparagraph Nominate Mountain Ash staff to the ASWWU President.
                    \subparagraph Supervise Mountain Ash staff, ensuring diligence and quality work.
                    \subparagraph Evaluate staff performance on a quarterly basis.
                    \subparagraph Coordinate with the ASWWU Marketing Vice President, the Collegian editor, the Mask editor, and the ASWWU Systems Manager regarding equipment.
                \paragraph[Communication]
                    \subparagraph Hold weekly Mountain Ash staff meetings to discuss progress, address issues, and determine goals.
                    \subparagraph Communicate progress and issues to the Marketing Vice President and the Media Board on a regular basis.
                    \subparagraph Establish a mentoring relationship and have monthly meetings with a faculty or community member that works in the design/publication field.
                \paragraph[Finance]
                    \subparagraph Work with the Financial Vice President to develop a budget for the year.
                    \subparagraph Monitor expenditures to ensure that they are within the budget.
                    \subparagraph Submit receipts for expenditures to the Financial Vice President within five (5) work days of purchase.
            \subsection[Basic Knowledge]
                \paragraph Basic knowledge of ASWWU's governing documents.
                \paragraph Have expertise in design principles.
            \subsection[Technical Skills]
                \paragraph Full knowledge of Adobe InDesign.
                \paragraph Full knowledge of Adobe Photoshop.
                \paragraph Full knowledge of Adobe Illustrator.

        \section[Head Photo Editor]
            \subsection The primary responsibility of the Head Photo Editor is to ensure that images are selected and edited for use by the various ASWWU departments. In this role the Head Photo Editor's primary responsibility is to manage the photo department unless it is absolutely necessary to work as a photographer. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Ensure that events taking place on and off campus that feature the students of WWU are captured in photographic medium.
                    \subparagraph Disseminate images to students via the ASWWU publications and other digital media outlets.
                    \subparagraph Manage Photo Department staff by hiring, delegating assignments, and evaluating progress.
                    \subparagraph Conduct quarterly performance evaluations with each employee.
                    \subparagraph Work with Risk and Safety Management to ensure that image usage meets current legal requirements.
                    \subparagraph Check that all images used in publications meet print standards.
                \paragraph[Organization]
                    \subparagraph Maintain up-to-date shared calendar.
                    \subparagraph Be accessible to ASWWU administration and publication staff.
                    \subparagraph Each week, sort event images into the appropriate network folder.
                \paragraph[Communication]
                    \subparagraph Conduct weekly meetings with photographers.
                    \subparagraph Conduct quarterly reviews of photographers and give feedback with the intent of fostering individual improvement
                    \subparagraph Collaborate with the Collegian Editor-in-Chief to ensure that the paper’s weekly image needs are fulfilled.
                    \subparagraph Collaborate with the Mountain Ash Editor to ensure the production of high-quality images that provide a comprehensive perspective of campus life
                \paragraph[Finance]
                    \subparagraph Monitor Photo Department expenditures to ensure they are within budget.
                    \subparagraph Purchase and maintain equipment as needed.
            \subsection[Basic Knowledge]
                \paragraph ASWWU governing documents.
                \paragraph Robert's Rules of Order.
                \paragraph Publications exposure.*
            \subsection[Technical Skills]
                \paragraph Adobe Photoshop.
                \paragraph Proficient with Microsoft Office Suite.
                \paragraph Adobe Bridge.
                \paragraph Apple Aperture.
                \paragraph Familiar with all photo equipment.
                \paragraph Adobe Illustrator.*

        \section[Videographer]
            \subsection The primary responsibility of the Videographer is to ensure that videos are shot and edited for use by the Marketing Department. In this role, the Videographer works to produce high-quality videos that reflect the vision and image of the ASWWU. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Work with Marketing Vice President to clarify the purpose and develop the concept of videos.
                    \subparagraph Distribute projects among the videographers to ensure each video is produced in a timely fashion.
                    \subparagraph Film, edit, and deliver video to appropriate locations.
                    \subparagraph Keep the camera and equipment in good working order and arrange for maintenance when necessary.
                    \subparagraph Conduct quarterly performance evaluations with staff.
                \paragraph[Communication]
                    \subparagraph Collaborate with Marketing Vice President to receive assignments.
                    \subparagraph Conduct weekly meetings with event videographers.
                    \subparagraph Conduct quarterly reviews of event videographers give feedback with the purpose of fostering individual improvement.
            \subsection[Basic Knowledge]
                \paragraph Video cameras.
                \paragraph DSLR cameras.
                \paragraph Video, image, audio formats.
                \paragraph Online video distribution methods.
            \subsection[Technical Skills]
                \paragraph The ability to edit quickly in either Sony Vegas, Apple Final Cut Pro, or Adobe Premier Pro.
                \paragraph Experience with Adobe Photoshop.
                \paragraph The ability to use a DSLR in manual mode. 
                
        \section[Human Resources Director]
            \subsection This position is responsible for serving ASWWU through up-to-date recordkeeping, efficient hiring and maintaining payroll as well as overseeing the overall wellbeing of ASWWU employees.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph[Recordkeeping]
                        \subsubparagraph Monitor, Edit and Distribute Department Manuals.
                        \subsubparagraph Review  and Update Job Descriptions.
                        \subsubparagraph Listen, Document and help resolve Employee Complaints.
                        \subsubparagraph Record and Manage Employee Evaluations.
                        \subsubparagraph Collect and Keep President's Annual Report.
                    \subparagraph[Hiring]
                        \subsubparagraph Plan and coordinate ASWWU Job Fair.
                        \subsubparagraph Ensure worker eligibility by working with Student Employment Services
                        \subsubparagraph Enter new hires into Peoplesoft HR.
                        \subsubparagraph Ensure proper paperwork is complete by working with WWU Payroll department.
                        \subsubparagraph Collect employee GPA waivers.
                        \subsubparagraph Conduct Orientation to ASWWU for all new hires.
                    \subparagraph[Payroll]
                        \subsubparagraph Monitor employee timecards and correct timecard changes in coordination with department head.
                \paragraph[Communication]
                    \subparagraph Report directly to the ASWWU President.
                    \subparagraph Has dotted-line reporting to the ASWWU sponsor.
                    \subparagraph Maintain communication with department heads in order to ensure all parties are completing their duties as defined in their Job Description.
            \subsection[Basic Knowledge]
                \paragraph Working knowledge of the ASWWU bylaws, particularly the Personnel Manual.
                \paragraph Have knowledge of harassment and discrimination, Title IX, hiring rules or potential issues and work with employees to avoid or resolve any issues.
                \paragraph Learn basic federal employment laws and have enough knowledge to answer questions when they arise.
        \section[Service Director]
            \subsection As an appointed member of ASWWU, this position is responsible for communicating various views of service of the student body to the ASWWU Cabinet, Walla Walla University's administration, and Center for Humanitarian Engagement (CHE). This position will pursue methods to implement service in all ASWWU's events. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Attend CHE's weekly meeting and report the updates to ASWWU.
                    \subparagraph Attend ASWWU's weekly meeting and report the updates to CHE.
                    \subparagraph Look for opportunities to create service-oriented events for ASWWU.
                    \subparagraph Find ways to implement service in existing ASWWU events.
                    \subparagraph Coordinate one care weekend. Date and details will be provided by CHE.
                    \subparagraph Represent ASWWU at CHE events when possible.
                    \subparagraph Conduct polls to find what service opportunities the student body desires to see on campus.
                \paragraph[Organization]
                    \subparagraph Maintain an up-to-date shared calendar between CHE, and ASWWU.
                \paragraph[Communication]
                    \subparagraph Communicate with the ASWWU Financial VP every other week.
                    \subparagraph Attend weekly Cabinet meetings.
                    \subparagraph Conduct a meeting with the Student Missions Coordinator every other week.
                    \subparagraph Work with Marketing VP and Collegian Editor-in-Chief to promote collaborative events between ASWWU and CHE.
                \paragraph[Finance]
                    \subparagraph Work with Financial VP to develop a budget for the year.
                    \subparagraph Monitor expenditures to ensure that they are within the budget.
                    \subparagraph Submit receipts for expenditures to the Financial VP within five (5) working days of purchase.
                \paragraph[Knowledge]
                    \subparagraph Basic Knowledge of ASWWU's governing documents.
                    \subparagraph Awareness and involvement with various student groups on campus.

    \article[Executive Staff]

    \section[\textit{Collegian} Head Layout Editor]
        \subsection This position is responsible for The Collegian's overall design, as well as managing all layout editors on staff. This position of service pursues changes that will improve the quality of student life on campus.
        \subsection[Responsibilities]
            \paragraph[Duties]
                \subparagraph Develop an encompassing theme and design for The Collegian in conjunction with the Editor-in-Chief.
                \subparagraph Create a template and establish specific design standards (e.g., fonts, photo captions, picture sizes, etc.).
                \subparagraph Supervise layout editors, ensuring diligence and quality work.
                \subparagraph Assist the Editor-in-Chief in design hiring decisions.
                \subparagraph Create a high-quality cover each week and work with Head Photo Editor as necessary to accomplish this goal.
                \subparagraph Collaborate with layout editors to ensure ads are placed effectively in each issue.
                \subparagraph Conduct quarterly performance evaluations with each layout editor.
            \paragraph[Organization]
                \subparagraph Maintain up-to-date shared calendar. 
                \subparagraph Maintain an organized Collegian file server and archives.
                \subparagraph Facilitate the creation and distribution of an internet version of The Collegian.
            \paragraph[Communication]
                \subparagraph Conduct quarterly reviews of layout editors and give feedback that will foster improvement.
        \subsection[Basic Knowledge]
            \paragraph Basic knowledge of the ASWWU governing documents.
        \subsection[Technical Skills]
            \paragraph Adobe InDesign.
            \paragraph Adobe Photoshop.
            \paragraph Adobe Illustrator.*
            \paragraph Mac OS.
            \paragraph Microsoft Windows.
            \paragraph Proficient with Microsoft Office Suite.

    \section[\textit{Collegian} Head Copy Editor]
        \subsection This position is responsible for establishing the grammatical standards used by The Collegian and ensuring that they are met. Additionally, this position supervises a team of copy editors. 
        \subsection[Responsibilities]
            \paragraph[Duties]
                \subparagraph Use the Associated Press Stylebook as a guide and create standards for headlines, abbreviations, etc.
                \subparagraph Work with the Editor-in-Chief to establish consistent submission deadlines for Section Editors.
                \subparagraph Assign articles to copy editors for proofreading.
                \subparagraph Supervise copy-editing process to ensure that articles are read by multiple copy editors before final edits.
                \subparagraph Assist the Editor-in-Chief in copy editor hiring decisions.
                \subparagraph Supervise copy editors, ensuring diligence and quality work.
                \subparagraph Read and sign off on each page of The Collegian before it is sent to print.
                \subparagraph Conduct quarterly performance evaluations with each copy editor.
            \paragraph[Organization]
                \subparagraph Maintain up-to-date shared calendar.
                \subparagraph Maintain regular office hours.
            \paragraph[Communication]
                \subparagraph Conduct quarterly reviews of copy editors and give feedback that will foster improvement.
        \subsection[Basic Knowledge]
            \paragraph Basic knowledge of the ASWWU governing documents.
            \paragraph Understand the principles of journalism.
        \subsection[Technical Skills]
            \paragraph Mac OS.
            \paragraph Microsoft Windows.
            \paragraph Proficient with Microsoft Office Suite.

    \section[\textit{Collegian} Section Editor]
        \subsection These positions (i.e. News, Sports, Features, Opinion, Religion, etc.) are responsible for producing quality sections to be published weekly in The Collegian. This position of service pursues changes that will improve the quality of student life on campus.
        \subsection[Responsibilities]
            \paragraph[Duties]
                \subparagraph Plan section structure for weekly use.
                \subparagraph Work with layout editor to establish a consistent style for pages.
                \subparagraph Develop a production timeline for section weekly.
                \subparagraph Adhere to the Society of Professional Journalists Code of Ethics.
                \subparagraph Provide deadlines, focus, and scope of articles to staff writers.
                \subparagraph Submit photo requests to the Head Photo Editor.
                \subparagraph Notify Head Copy Editor of weekly content.
                \subparagraph Make changes suggested by copy editors before final edits. 
                \subparagraph Clear any variations to the changes with copy editors.
                \subparagraph Conduct quarterly performance evaluations with each staff writer.
            \paragraph[Organization]
                \subparagraph Maintain up-to-date shared calendar.
            \paragraph[Communication]
                \subparagraph Meet regularly with Editor-in-Chief to discuss content, progress, address issues, and determine goals.
                \subparagraph Conduct quarterly reviews of staff writers and give feedback that will foster improvement.
        \subsection[Basic Knowledge]
            \paragraph Basic knowledge of ASWWU governing documents.
            \paragraph Understand the principles of journalism.
        \subsection[Technical Skills]
            \paragraph Mac OS.
            \paragraph Microsoft Windows.
            \paragraph Proficient with Microsoft Office Suite. 

    \section[\textit{Collegian} Layout Editor]
        \subsection This position is responsible for the layout and design of pages for The Collegian each week. This position of service pursues changes that will improve the quality of student life on campus.
        \subsection[Responsibilities]
            \paragraph[Duties]
                \subparagraph Complete assignments from Head Layout Editor and Editor-in-Chief.
                \subparagraph Establish recurring structure throughout pages.
                \subparagraph Follow design template and design standards established by the Head Layout Editor.
                \subparagraph Collaborate with section editors to ensure pages have an appropriate amount of content.
                \subparagraph Clear photo captions with Head Photo Editor.
            \paragraph[Organization]
                \subparagraph Maintain up-to-date shared calendar.
            \paragraph[Communication]
                \subparagraph Collaborate with Section Editors to ensure pages have an appropriate amount of content.
                \subparagraph Work with Head Photo Editor to receive photos for pages.
        \subsection[Basic Knowledge]
            \paragraph Basic knowledge of the ASWWU governing documents.
            \paragraph Understand the principles of design.
        \subsection[Technical Skills]
            \paragraph Adobe InDesign.
            \paragraph Adobe Photoshop.
            \paragraph Adobe Illustrator.*
            \paragraph Mac OS.
            \paragraph Microsoft Windows.
            \paragraph Proficient with Microsoft Office Suite. 

    \section[\textit{Collegian} Copy Editor]
        \subsection This position is responsible for ensuring that the grammatical standards set forth by the Head Copy Editor to be used by The Collegian are met. This position of service pursues changes that will improve the quality of student life on campus.
        \subsection[Responsibilities]
            \paragraph[Duties]
                \subparagraph Complete assignments from Head Copy Editor and Editor-in-Chief.
            \paragraph[Organization]
                \subparagraph Maintain up-to-date shared calendar.
            \paragraph[Communication]
                \subparagraph Collaborate with section editors to ensure they have an appropriate understanding of grammatical standards.
        \subsection[Basic Knowledge]
            \paragraph Basic knowledge of ASWWU governing documents. 
            \paragraph Understand the principles of journalism.
        \subsection[Technical Skills]
            \paragraph Mac OS.
            \paragraph Microsoft Windows.
            \paragraph Proficient with Microsoft Office Suite.

    \section[\textit{Collegian} Distributor/Office Manager]
        \subsection This position is responsible for the delivering The Collegian to frequently visited locations around the WWU campus on a weekly basis. This position of service pursues changes that will improve the quality of student life on campus.
        \subsection[Responsibilities]
            \paragraph[Duties]
                \subparagraph Purchase food for the Collegian staff each Wednesday evening.
                \subparagraph Distribute The Collegian to strategic locations across campus.
            \paragraph[Organization]
                \subparagraph Maintain up-to-date shared calendar.
                \subparagraph Maintain a list detailing how many copies of The Collegian are to be distributed to each location.
            \paragraph[Communication]
                \subparagraph Meet with Editor-in-Chief to discuss distribution of The Collegian and the staff’s food needs.
            \paragraph[Finance]
                \subparagraph Know budgets for staff maintenance and spend within that budget
                \subparagraph Keep receipts and fill out a reimbursement form each week, with signatures from Editor-inChief and Financial Vice President.
        \subsection[Basic Knowledge]
            \paragraph Basic knowledge of the ASWWU governing documents.
        \subsection[Technical Skills]
            \paragraph Proficient with Microsoft Office Suite.

    \section[Systems Manager]
        \subsection As an appointed member of the ASWWU, this position is responsible for maintaining all electronic equipment related to the ASWWU and its departments.
        \subsection[Responsibilities]
            \paragraph[Duties]
                \subparagraph Create and manage user directories and files on client and server platforms.
                \subparagraph Monitor, tune, diagnose, and resolve operating system problems on client platform.
                \subparagraph Purchase hardware, software, and equipment in compliance with the ASWWU Bylaws.
                \subparagraph Provide technical assistance to all ASWWU departments.
            \paragraph[Organization]
                \subparagraph Maintain regular office hours.
                \subparagraph Maintain accurate asset management records and sufficient software licenses.
                \subparagraph Archive and back up files weekly.
                \subparagraph Maintain up-to-date shared calendar.
            \paragraph[Communication]
                \subparagraph Discuss equipment needs with the ASWWU Marketing Vice President and the editors of the \textit{Mountain Ash}, \textit{The Collegian}, and the \textit{Mask}, and the managers of ASWWU Television.
            \paragraph[Finance]
                \subparagraph Research requested equipment purchases.
                \subparagraph File all warranties in the main ASWWU office.
                \subparagraph Work with the Financial Vice President to establish a working budget.
                \subparagraph Monitor expenditures to ensure that they are within the budget.
                \subparagraph Submit receipts for expenditures to the Financial Vice President within five (5) work days of purchase.
        \subsection[Basic Knowledge]
            \paragraph Basic knowledge of ASWWU’s governing documents. 
        \subsection[Technical Skills]
            \paragraph Proficiency in:
                \subparagraph Macintosh computers.
                \subparagraph PCs.
                \subparagraph OS X Client and Server.
                \subparagraph RAID.
                \subparagraph Microsoft Windows.
                \subparagraph Mac OS
                \subparagraph Adobe InDesign.
                \subparagraph Adobe Photoshop.
                \subparagraph Adobe Illustrator.
            \paragraph Familiar with Unix/Linux
            \paragraph Proficient with Microsoft Office Suite. 

    \section[Webmaster]
        \subsection This position is responsible for maintaining the ASWWU website. The website is expected to keep the student body and other audiences up to date with current ASWWU happenings. This position of service pursues changes that will improve the quality of student life on campus.
        \subsection[Responsibilities]
            \paragraph[Duties]
                \subparagraph Actively update the ASWWU website and its affiliates to reflect current information, improve attractiveness, and increase hits.
                \subparagraph Ensure the online voting system is maintained for use in ASWWU elections
                \subparagraph Maintain availability of the ASWWU Digital Senate Archive in accordance with Title I, Article V, Section 5 of the Bylaws.
            \paragraph[Organization]
                \subparagraph Maintain a document outlining the structure of the website so that the incoming webmaster can easily make modifications and solve issues.
                \subparagraph Maintain up-to-date shared calendar.
            \paragraph[Communication]
                \subparagraph Campus Relations
                    \subsubparagraph Work with Information Services to address any issues that relate to the Walla Walla University technology infrastructure and network
                \subparagraph Internal Relations
                    \subsubparagraph Collaborate with Marketing Vice President to receive assignments.
                    \subsubparagraph Provide written instructions and verbally instruct the appropriate ASWWU personnel how to post content to the website.
        \subsection[Basic Knowledge]
            \paragraph Basic knowledge of ASWWU governing documents.
            \paragraph Understand basic design principles.
        \subsection[Technical Skills]
            \paragraph Proficient with Microsoft Office Suite.
            \paragraph Typo3.**
            \paragraph PHP.**
            \paragraph MySQL.
            \paragraph Adobe Flash. 

    \section[Tread Shed Manager]
        \subsection This position is responsible for maintaining the ASWWU bicycles on campus and making sure that any new bicycles that are purchased are ready for campus-wide use.
        \subsection[Responsibilities]
            \paragraph Duties
                \subparagraph Maintain the Tread Shed facility.
                \subparagraph Fix any broken ASWWU bicycles.
                \subparagraph Assist students with fixing their personal bikes when brought into the Tread Shed.
                \subparagraph Maintain the Golf Carts and keep them available when needed. 
            \paragraph[Organization]
                \subparagraph Maintain regular office hours every week.
                \subparagraph Make schedule available to other students.
            \paragraph[People]
                \subparagraph Hire on assistants as needed in accordance with the hiring procedure outlined in Title I, Article II.
            \paragraph[Communication]
                \subparagraph Report to and communicate with ASWWU President and Financial VP as needed.
                \subparagraph Communicate with any students the costs of any parts that will be needed to fix a bicycle.
            \paragraph[Financial]
                \subparagraph Research price and efficiency of potential bikes.
                \subparagraph Coordinate with President and Financial VP during any purchases.
        \subsection[Basic Knowledge]
            \paragraph Know the mechanics of how a bicycle works.
            \paragraph Know the general mechanics of how a golf cart works.
        \subsection[Technical Skills]
            \paragraph Have proper understanding and skill with the tools required to maintain bicycles and golf carts. 

    \article[Legislative]
        \section[Senate Secretary]
            \subsection As a member of the legislative branch of the ASWWU, this position is responsible for recording minutes for Senate and its subcommittees.
            \subsection[Responsibilities]
                \paragraph Duties
                    \subparagraph Take detailed, legible minutes at Senate and its subcommittees.
                    \subparagraph Prepare to take minutes at any meeting where required to take minutes.
                    \subparagraph Arrive early to meetings to help set up and stay after to clean up.
                    \subparagraph Review incoming bills for clerical errors.
                \paragraph[Organization]
                    \subparagraph Tracks all meetings dates and times.
                \paragraph[Communication]
                    \subparagraph Work with Executive Vice President to determine time of weekly Senate meetings.
            \subsection[Basic Knowledge]
                \paragraph In-depth knowledge of ASWWU’s governing documents.
            \subsection[Technical Skills]
                \paragraph Proficient with Microsoft Office Suite.
                \paragraph Understand proper minute formatting. 

        \section[Senator]
            \subsection As a member of the legislative branch of the ASWWU, this position is responsible for representing the needs and requests of the student body to the ASWWU. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Attend all Senate meetings. 2.2.1.1.1. Portland campus Senator may attend via conference call or other electronic means.
                    \subparagraph Make informed voting decisions based upon Senate discussion and constituent views.
                    \subparagraph Raise questions regarding questionable actions by the ASWWU.
                    \subparagraph Serve on one (1) of the four (4) subcommittees (Finance Committee, Governance Committee, Personnel Committee, and Review Committee) according to Senate Procedural Rules Article II, Section 3.
                    \subparagraph Volunteer to represent the ASWWU at events.
                \paragraph[Organization]
                    \subparagraph File all Senate documents in the binder provided by the Senate Chair. 
                \paragraph[People]
                    \subparagraph Contact constituents on a weekly basis, documenting contact and issues raised.
                    \subparagraph Encourage constituents to attend Senate meetings.
                \paragraph[Communication]
                    \subparagraph Communicate constituent concerns to the Senate.
                    \subparagraph Provide weekly feedback back to constituents after Senate discussion.
                \paragraph[Financial]
                    \subparagraph Monitor the ASWWU budget, raising questions about allocations and expenditures as necessary.
                    \subparagraph Hold the Executive branch fiscally accountable.
                    \subparagraph Approve all capital expenditures in accordance with the ASWWU Bylaws.
            \subsection[Basic Knowledge]
                \paragraph In-depth knowledge of ASWWU's governing documents.
                \paragraph Working knowledge of Robert's Rules of Order. 

    \article[Judicial]
        \section[Parliamentarian/Chief Justice]
            \subsection As a member of the judicial branch of the ASWWU organization, this position is responsible for maintaining Senate order and providing a balance for the executive and legislative branches of the ASWWU. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Maintain parliamentary order during designated meetings and make procedural decisions as requested.
                    \subparagraph Give procedural guidance to the executive committee.
                    \subparagraph Update the ASWWU documents following Senate decisions.
                    \subparagraph Prepare Senate bills for signatures by the Senate Chair and ASWWU President within five (5) business days of passing.
                    \subparagraph Provide guidance to Senators on parliamentary procedures.
                    \subparagraph Veto, in conjunction with other justices, any action by ASWWU's Executive Branch or Senate that is not in line with the ASWWU's governing documents.
                    \subparagraph Chair weekly Judicial Committee meetings, reviewing all bills passed by Senate.
                    \subparagraph Interpret, in conjunction with other justices, the ASWWU governing documents when questions arise.
                    \subparagraph Chair impeachment proceedings.
                \paragraph[Organization]
                    \subparagraph Archive official Senate business.
                \paragraph[People]
                    \subparagraph Present candidates applying for Justice positions to Senate.
                    \subparagraph Monitor Justices' performance, evaluating performance on a quarterly basis.
                \paragraph[Communication]
                    \subparagraph Provide written documentation of all decision made by the Judicial Committee to Senate.
            \subsection[Basic Knowledge]
                \paragraph Have a working knowledge of Robert's Rules of Order.
                \paragraph In-depth knowledge of the ASWWU governing documents.
            \subsection[Technical Skills]
                \paragraph Proficient with Microsoft Office Suite. 

        \section[Justice]
            \subsection As a member of the judicial branch of the ASWWU organization, this position is responsible for balancing the executive and legislative branches of the ASWWU. This position of service pursues changes that will improve the quality of student life on campus.
            \subsection[Responsibilities]
                \paragraph[Duties]
                    \subparagraph Veto, in conjunction with other justices, any action by ASWWU's Executive Branch or Senate that is not in line with the ASWWU governing documents.
                    \subparagraph Attend weekly Judicial Committee meetings.
                    \subparagraph Interpret the ASWWU governing documents when questions arise in conjunction with other justices.
                    \subparagraph Attend impeachment proceedings and aid the Chief Justice.
            \subsection[Basic Knowledge]
                \paragraph Have a working knowledge of Robert's Rules of Order.
                \paragraph In-depth knowledge of the ASWWU governing documents.
            \subsection[Technical Skills]
                \paragraph Proficient with Microsoft Office Suite.

    \vspace{5mm}

    * \textit{These items are not required but recommended}\\
    \*** \textit{Absolutely necessary}

\miscsection[Appendix C: Presidential Annual Report]
\section The annual report from the ASWWU president will include the following items,
\begin{itemize}
\item Table of Contents
\item Basic Description of ASWWU, with Mission, Budget, Constituency, Organizational Structure, and
\item Representation to AIA, WWU, NAD…
\item A Departmental Breakdown
\item Budget and Actuals
\item Current ASWWU Positions (Descriptions \& Names)
\item Calendar of Events with Descriptions
\item Services \& Missions
\item Projects \& Initiatives (Succeeded \& Failed)
\item Standing Agreements Made and/or Modified this Year (Dates and Descriptions)
\item Collaborations with Outside Organizations
\item Committees \& Groups
\item Relevant Documents
\item Appendices with Bills from Senate, Representative Docs, Proposals, Contracts
\item Pictures (Designs)
\item What Could Be Done Better? 
\end{itemize}

\end{document}
